A Large-scale Study of Polymorphism in R

### 2019-03-24 paper/main.tex
a few examples, more to come. waiting on latest prl3 run results

@@

In terms of programmer behaviour, we observe a pattern of optional arguments throughout several R packages, wherein programmers specify a default argument value which is sometimes NULL.
Consider the snippet in Figure~\ref{fig:optnull} for an example.
\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
# w here is weights
frac.ranks <- function(x, w=NULL) {
  if (is.null(w)) w <- rep(1, length(x)) # if no weights passed, take all weights = 1
  ...
  \end{lstlisting}}\caption{Example of optional argument.}\label{fig:optnull}\end{figure}
The distinction between NULL and other types is not particularly useful to the programmer, so we propose to also collapse this distinction.

>>>>

\AT{Collection of examples of polymorphism...}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
# w here is weights
frac.ranks <- function(x, w=NULL) {
  if (is.null(w)) w <- rep(1, length(x)) # if no weights passed, take all weights = 1
  ...
\end{lstlisting}}\caption{Example of optional argument (from {\tt acid} package).}\label{fig:optnull}\end{figure}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
is.point.inside <- function (point, polyg) {
    p <- as.numeric(point) # as.numeric(list(1, 2)) => c(1, 2)
    ...
\end{lstlisting}}\caption{Example of list/vector argument (from {\tt bivrp} package).}\label{fig:listvec}\end{figure}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
function (object, fn = mean, par.name, comp.label, chain.no,  ...) 
{
    ...
    if (is.character(fn)) {
        if (fn == "MODE" | fn == "MAP") {
            do_MAP <- TRUE
        }
        else {
            do_MAP <- FALSE
            fn <- match.fun(fn) # looks up the function name
        }
    }
    ...
\end{lstlisting}}\caption{Example of char/closure argument (from {\tt BAMBI} package).}\label{fig:charclos}\end{figure}

\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
nret.translator <- function(dat, spss="out", ...){
  ...
  if(identical(spss, "out")) {
    if(!is.vector(dat)) {
        stop(simpleError("If 'corr=TRUE', 'dat' must be a vector!"))
      }
    ...
  } else {
    ...
    # here, dat is data.frame
    items.idx <- items.idx[order(names(dat[, items.idx]))]
  }

\end{lstlisting}}\caption{Example of data.frame/vector/double argument (from {\tt klausR} package).}\label{fig:charclos}\end{figure}

@@

In terms of programmer behaviour, we observe a pattern of optional arguments throughout several R packages, wherein programmers specify a default argument value which is sometimes NULL.
Consider the snippet in Figure~\ref{fig:optnull} for an example.
\AT{TODO put that figure here}
The distinction between NULL and other types is not particularly useful to the programmer, so we propose to also collapse this distinction.
